Examples in R* paper

### 2020-03-17 src/s_examples.Rmd
ms nearly there -- just needs to have mvt normal section completed

# Multivariate normal

Fit model in Stan
```{r}
N <- 250
A <- rWishart(1, 250, diag(N))[,,1]
model <- stan_model("mvt_250.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=200, chains=4)
print(fit)
```

```{r}
full_data <- rstan::extract(fit, permuted=F)
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = 252)
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:251] <- full_data[j, i, ]
    m_flattened[k, 252] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V252) %>% 
  mutate(chain=as.factor(chain))

@@

plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))
varImp(gbmFit1)
```

>>>>

# Multivariate normal
Fit model in Stan with 10000 iterations
```{r}
N <- 250
# A <- rWishart(1, 250, diag(N))[,,1]
model <- stan_model("mvt_250.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=10000, chains=4, thin=5)
print(fit)
saveRDS(fit, "../output/mvt_fit_10000.rds")

full_data <- rstan::extract(fit, permuted=F)
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = 252)
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:251] <- full_data[j, i, ]
    m_flattened[k, 252] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V252) %>% 
  mutate(chain=as.factor(chain))

@@

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}

a_df <- tibble(samples_5000=colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
```

With 400 iterations
```{r}
fit <- sampling(model, data=list(N=N, A=A), iter=400, chains=4)
print(fit)
saveRDS(fit, "../output/mvt_fit_400.rds")

full_data <- rstan::extract(fit, permuted=F)
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = 252)
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:251] <- full_data[j, i, ]
    m_flattened[k, 252] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V252) %>% 
  mutate(chain=as.factor(chain))

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}

a_df <- a_df %>%
  mutate(samples_400=colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))
```

```{r}
model <- stan_model("mvt_250_ncp.stan")
fit <- sampling(model, data=list(N=N, A=A), iter=10000, chains=4, thin=5)
print(fit)
saveRDS(fit, "../output/mvt_ncp_fit_10000.rds")

full_data <- rstan::extract(fit, permuted=F)
nparams <- dim(full_data)[3]
m_flattened <- matrix(nrow = nrow(full_data) * 4, ncol = (nparams + 1))
k <- 1
for(i in 1:4){
  for(j in 1:nrow(full_data)){
    m_flattened[k, 1:nparams] <- full_data[j, i, ]
    m_flattened[k, (nparams + 1)] <- i
    k <- k + 1
  }
}
m_flattened <- m_flattened %>% 
  as.data.frame() %>% 
  rename(chain=V502) %>% 
  mutate(chain=as.factor(chain))
n_distinct(m_flattened$chain)

plda <- predict(object=gbmFit1, newdata=testing_data)
tibble(predicted=plda, actual=testing_data$chain) %>% 
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct))

mAccuracy <- matrix(nrow = nrow(plda),
                    ncol = nsim)
for(i in 1:nsim){
  for(j in 1:nrow(plda)){
    mAccuracy[j, i] <- if_else(which(rmultinom(1, 1, prob = plda[j, ])==1)==testing_data$chain[j], 1, 0)
  }
}

a_df <- a_df %>%
  mutate(samples_10000_ncp=colMeans(mAccuracy)/(1/n_distinct(training_data$chain)))

saveRDS(a_df, "../output/mvt_fit_all_accuracy.rds")

g <- 
  a_df %>% 
  select(samples_400, samples_10000_ncp) %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of samples", labels=c("400", "2000", "5000")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"))
# ggsave("../output/mvt_three.pdf", g, width = 8, height = 6)
```
